Visualizing Physical Query Execution in a Relational Big Data Management System

### 2014-02-26 progress-report/project_plan.tex
added more milestones

\begin {itemize}
    \item Umar Javed: visualizing network data flow between workers
    \item Thierry Moreau: visualizing query plan
    \item Dominik Moritz: team leader, in charge of data collection and back end
    \item Adriana Szerkes: visualizing query fragment execution
\end{itemize}

>>>>

\begin {itemize}
    \item Umar Javed: visualizing network data flow between workers
    \item Thierry Moreau: visualizing query plan
    \item Dominik Moritz: architect, data collection and back end
    \item Adriana Szerkes: visualizing query fragment execution
\end{itemize}

\subsection{Milestones}

\paragraph{Current Prototype}

\paragraph{Milestones}

\begin{enumerate}
    \item Project Planning (completed Feb 23rd)
    \begin{enumerate}
        \item Brainstorming and goals
        \item List questions we'd like to answer
        \item Develop a consistent story-board
        \item Assign responsibilities
    \end{enumerate}
    \item Initial System Setup \& Specifications (completed Feb 23rd)
    \begin{enumerate}
        \item Set up cluster \& web front-end
        \item Data collection from query-runs
        \item Formalize interfaces and data formats
    \end{enumerate}
    \item Initial Prototype (complete by March 5th)
    \begin{enumerate}
        \item Produce initial visualizations
        \item Add a basic interaction between views
    \end{enumerate}
    \item Working Prototype (complete by March 13th)
    \begin{enumerate}
        \item Improve visualizations and interaction
    \end{enumerate}
    \item Project Deliverables 
    \begin{enumerate}
        \item Produce poster (complete by March 13th)
        \item Complete demo (complete by March 13th)
        \item Write the project report (complete by March 20th)
    \end{enumerate}

\end{enumerate}
